HPC--101\\Onboarding

### 2024-01-18 hpc_101/sections/01_intro.tex
workspace info to TBD
update to slides for onboarding

\section[University of Hawai'i High Performance Compute Cluster]{University of Hawai'i High Performance Compute Cluster}
\begin{frame}
    \frametitle{University of {\hawaii} High Performance Compute Cluster}
    \begin{itemize}
    \item The University~of~{\hawaii} High Performance Compute Cluster - \textbf{\mana} is \textbf{free} to use for all active faculty, staff, and students affiliated with the University of {\hawaii}
    \item Community acquired nodes are equally accessible to all users
    \item Nodes purchased through the {\textbf{condo program}} are shared with the community, but priority is given to the node owner and their agents
		\item Nodes may be {\textbf{leased}} from the community pool
		\item Additional permanent storage can be leased by faculty \& staff
    \end{itemize}
		\begin{block}{Mana Resource Summary}
  \begin{table}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{l||l||l||l||l||l||l||l}
      %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\ 
			\toprule

              {}               & \thead{\textbf{Nodes}} & \thead{\textbf{CPU Cores}} & \thead{\textbf{Memory}} & \thead{\textbf{GPUs}} & \thead{\textbf{Home/Group Space}} & \thead{\textbf{Scratch Space}} & \thead{\textbf{Storage for lease}} \\ 
							\midrule  \midrule %\hline
        \thead{\textbf{Total}} & 366                    & 9,396                      & 67.3 TB                   &  120                   & 80 TB                             &  111 TB                        & 1 PB              \\ %\hline
				\bottomrule
      \end{tabular}%
    }
  \end{table}
	\end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{Permanent Storage}
  \begin{enumerate}
  \item Home Storage
    \begin{itemize}
    \item {\textbf{Purpose}}: Personal storage for applications and active data that needs to persist on {\mana}
    \end{itemize}
  \item Group/Lab Storage
    \begin{itemize}
    \item {\textbf{Purpose}}: Group/Lab storage allows users to share data \& applications with a need for persistence on {\mana}
    \item PI must contact \textbf{uh-hpc-help@lists.hawaii.edu} to set up group/lab storage
    \end{itemize}
  \end{enumerate}
~\\
  Permanent storage options on {\mana} have the following attributes:
  \begin{itemize}
  \item 50 GB default quota with a max quota of 300 GB
  \item Quota increases are re-evaluated annually
  \item Available on all nodes
  \item Freely available to users
  \end{itemize}

@@

\begin{frame}
  \frametitle{Scratch Storage}
  \begin{enumerate}
    \item {\lustre}
      \begin{itemize}
			\item A parallel distributed file system 
      \end{itemize}
    \item NFS
      \begin{itemize}
			\item A distributed file system 
      \end{itemize}
  \end{enumerate}
~\\
  Scratch file systems on {\mana} have the following attributes:
  \begin{itemize}
	\item 5 TB quota
  \item \textbf{Purge policy} -- 20 days based on file modify time
  \item Available on all nodes
  \item Freely available to users
  \end{itemize}

@@

%\begin{frame}
  %\frametitle{For Fee Storage}
  %\begin{enumerate}
    %\item ValueStorage
      %\begin{itemize}
      %\item Enterprise class equipment 
      %\item 10 Gbit connected to the UH-HPC
      %\item Currently only accessible on the DTNs and login nodes
      %\end{itemize}
    %\item LTS  
      %\begin{itemize}
      %\item Cheap-n-Deep
      %\item 100 Gbit connected to the UH-HPC
      %\item Accessible on all nodes
      %\end{itemize}
  %\end{enumerate}
%\end{frame}

>>>>

%\section[Terminology]{Terminology}

%\begin{frame}
	%\frametitle{Terminology}
	%\begin{itemize}
	%\item \textbf{Node} -- Another name for a server or computer
        %\item \textbf{Login node} -- A specialized node that users connect to in order to submit work to a computer cluster
        %\item \textbf{Computer cluster} -- A set of loosely or tightly connected nodes that work together so that, in many respects, they can be viewed as a single system\footnote{\label{wiki_ccluster}\tiny\url{https://en.wikipedia.org/wiki/Computer_cluster}}
        %\item \textbf{Data transfer node (DTN)} -- Specialized nodes that minimize the impedance on the network to access the full capability of the network
	%\item \textbf{Science DMZ (SciDMZ)} --  A portion of the network configured with equipment and security policies in order to optimize for high-performance scientific applications rather than for general-purpose business systems or “enterprise” computing 
	%\item \textbf{Multi-factor Authentication (MFA)} -- An authentication method in which a computer user is granted access only after successfully presenting two or more pieces of evidence or factors to an authentication mechanism, e.g., DUO
%
	%\end{itemize}
%\end{frame}

%\begin{frame}
	%\frametitle{Terminology}
	%\begin{itemize}
	%\item \textbf{Symbolic Link (symlink)} -- A file that contains a reference to another file or directory
	%\item \textbf{Command-line interface/interpreter (CLI)} -- A text-based user interface used to view and manage computer files 
	%\item \textbf{Message Passing Interface (MPI)} -- A standard that is used by programs to pass messages between nodes
	%\item \textbf{High Performance Compute (HPC)} -- A computing paradigm in which applications are typically a tightly coupled parallel job that benefit from a low-latency interconnect
	%\item \textbf{High Throughput Compute (HTC)} -- A computing paradigm that focuses on the efficient execution of a large number of loosely-coupled tasks
        %\item \textbf{Modified time} -- The last time the file was modified (content has been modified)\footnote{\label{Types of timestamps}\tiny\url{https://unix.stackexchange.com/a/2465}}
        %\item \textbf{Shell script (script)} -- A computer program designed to be run by a CLI\footnote{\label{Shell script}\tiny\url{https://en.wikipedia.org/wiki/Shell_script}}
        %\item Pleasantly Parallel -- Processes are independent and no communication is necessary 
	%\end{itemize}
%
%
%\end{frame}
%

\section[University of Hawai'i High Performance Compute Cluster]{University of Hawai'i High Performance Compute Cluster}
\begin{frame}
    \frametitle{University of {\hawaii} High Performance Compute Cluster}
    \begin{itemize}
    \item The University~of~{\hawaii} High Performance Compute Cluster - \textbf{\mana} is \textbf{free} to use for all active faculty, staff, and students affiliated with the University of {\hawaii}
    \item Community acquired nodes are equally accessible to all users
    \item Nodes purchased through the {\textbf{condo program}} are shared with the community, but priority is given to the node owner and their agents
		\item Nodes may be {\textbf{leased}} from the community pool
		\item Additional permanent storage can be leased by faculty \& staff
    \end{itemize}
		\begin{block}{Koa Resource Summary}
  \begin{table}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{l||l||l||l||l||l||l||l}
      %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\ 
			\toprule

              {}               & \thead{\textbf{Nodes}} & \thead{\textbf{CPU Cores}} & \thead{\textbf{Memory}} & \thead{\textbf{GPUs}} & \thead{\textbf{Home Space}} & \thead{\textbf{Scratch Space}} & \thead{\textbf{Storage for lease}} \\ 
							\midrule  \midrule %\hline
        \thead{\textbf{Total}} & 269                    & 7,501                      & 53 TB                   &  146                   & 50 GB per user                             &  800 TB                        & 2 PB              \\ %\hline
				\bottomrule
      \end{tabular}%
    }
  \end{table}
	\end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{Permanent Storage}
  \begin{enumerate}
  \item Home Storage
    \begin{itemize}
    \item {\textbf{Purpose}}: Personal storage for applications and active data that needs to persist on {\mana}
		\item {\textbf{Quota}}: 50 GB per user
    \end{itemize}
  \item Lab Storage
    \begin{itemize}
    \item {\textbf{Purpose}}: Lab storage allows users to share data \& applications with a need for persistence on {\mana}
		\item {\textbf{Quota}}: 500 GB and 512,000 files/folders (inodes)
    \end{itemize}
  \end{enumerate}
~\\
  Permanent storage options on {\mana} share the following attributes:
  \begin{itemize}
  \item Available on all nodes
  \item Freely available to users
  \end{itemize}

@@

\begin{frame}
  \frametitle{Scratch Storage}
  \begin{enumerate}
    \item {\lustre}
      \begin{itemize}
			\item A parallel distributed file system 
      \end{itemize}
    %\item NFS
      %\begin{itemize}
			%\item A distributed file system 
      %\end{itemize}
  \end{enumerate}
~\\
  Scratch file systems on {\mana} have the following attributes:
  \begin{itemize}
	\item 800 TB and 400K file/folder (inode) quota shared by all users
  \item \textbf{Purge policy} -- 90 days based on file modify time
  \item Available on all nodes
  \item Freely available to users
  \end{itemize}

@@

\begin{frame}
  \frametitle{Storage as a Service}
  \begin{enumerate}
    \item KoaStore
      \begin{itemize}
      \item \textbf{{Purpose:}} Additional permanent storage for applications and active data on {\mana}.
			\item \$50/TB/year
			\item Purchased in year increments
			\item Available on all nodes
      \end{itemize}
    \item KoaCloud
      \begin{itemize}
      \item \textbf{{Purpose:}} Dropbox/Google Drive like storage that can be used outside of {\mana} for research data.
			\item \$55/TB/year
			\item Purchased in year increments
      \end{itemize}
  \end{enumerate}
\end{frame}

### 2024-01-18 hpc_101/sections/03_policies.tex
Removed account purge policy
update to slides for onboarding

\section[Mana Usage Policies]{Mana Usage Policies}

\subsection{Login nodes \& DTN nodes}
\begin{frame}
\frametitle{Login nodes \& DTN nodes}
\begin{block}{}
The following actions are acceptable on the shared systems in {\mana}:
\begin{enumerate}
\item File/Directory management [ Login \& DTN nodes ]
\item Text editing with a text editor: vi/vim, emacs, nano [ Login \& DTN nodes ]
\item Transferring files to and from the cluster (scp, rsync, SFTP, globus, aspera, lftp, etc.) [ Login \& DTN nodes ]
\item Shall be used to submit batch and interactive jobs [Login nodes]
\item SSH shell access [ Login \& DTN nodes ]
\end{enumerate}
\end{block}

@@

\subsection{Storage Policy}
\begin{frame}
\frametitle{Storage Policy}
\begin{enumerate}
\item ITS is not responsible for any data that is deleted or loss due to user error, hardware failure, administrator error.  Users are responsible for their own data and are highly encouraged to backup data that is important to them at other storage locations
\item Files located on the scratch file systems are subject to a \textbf{20 day} purge policy that is based on the file/directory modified timestamp.  \textbf{Files that are purge cannot be recovered}.  Users are encouraged to copy their results off the scratch file system as soon as possible upon completion of their job
\item  Home storage currently snapshots once a day per user in case of accidental file deletion
\end{enumerate}
\end{frame}
%\btVFill
%\begin{center}
%\footnotesize \textbf{\emph{Login node usage policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
%\end{center}

\subsection{User Account Life Cycle}
\begin{frame}
\frametitle{User Account Life Cycle}
\begin{enumerate}
\item Accounts that are idle for 120 days will be locked
\item Accounts that have been locked can be unlocked upon request with no further action then emailing us a request to unlock their account
\item Accounts that are idle for a total of 180 days will be purged from the cluster
\item Users that have been purged may request a reactivation of their account, but may be required to take a quiz to confirm retention of how to use {\mana}
\item Users that will be leaving UH or are no longer active at UH, will need to have an active UH faculty/staff member in good standing, request a {\mana} account extension.
\end{enumerate}
\end{frame}

>>>>

\section[Koa Usage Policies]{Koa Usage Policies}

\subsection{Login nodes}
\begin{frame}
\frametitle{Login nodes}
\begin{block}{}
The following actions are acceptable on the login nodes of {\mana}:
\begin{enumerate}
\item File/Directory management
\item Text editing with a text editor: vi/vim, emacs, nano
\item Transferring files to and from the cluster (scp, rsync, SFTP, etc.)
\item Submit batch and interactive jobs
\item SSH shell access
\end{enumerate}
\end{block}

@@

\subsection{Storage Policy}
\begin{frame}
\frametitle{Storage Policy}
\begin{enumerate}
\item ITS is not responsible for any data that is deleted or loss due to user error, hardware failure, administrator error.  Users are responsible for their own data and are highly encouraged to backup data that is important to them at other storage locations
\item Files located on the scratch file systems are subject to a \textbf{90 day} purge policy that is based on the file/directory modified timestamp.  \textbf{Files that are purge cannot be recovered}.  Users are encouraged to copy their results off the scratch file system as soon as possible upon completion of their job
\item  Home storage currently snapshots once a day per user in case of accidental file deletion
\end{enumerate}
\end{frame}
%\btVFill
%\begin{center}
%\footnotesize \textbf{\emph{Login node usage policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
%\end{center}

\subsection{User Account Life Cycle}
\begin{frame}
\frametitle{User Account Life Cycle}
\begin{enumerate}
\item Accounts that are idle for 120 days will be locked
\item Accounts that have been locked can be unlocked upon request with no further action then emailing us a request to unlock their account
%\item Accounts that are idle for a total of 180 days will be purged from the cluster
%\item Users that have been purged may request a reactivation of their account, but may be required to take a quiz to confirm retention of how to use {\mana}
\item Users that will be leaving UH or are no longer active at UH, will need to have an active UH faculty/staff member in good standing, request a {\mana} account extension.
\end{enumerate}
\end{frame}
